\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{enumitem}
\geometry{margin=1in}

\title{Equations and Functions Practice}
\author{}
\date{}

\begin{document}
\maketitle

\section*{Definitions}
Domain: the set of all input values $x$ for which a function is defined.

Range: the set of all output values $y$ the function can produce.

\vspace{0.4em}
\noindent Example (table of values): $(-1,2),(0,2),(1,1),(2,4)$.\\
Domain $=\{-1,0,1,2\}$, Range $=\{1,2,4\}$.

\section*{Problems}
\begin{enumerate}[leftmargin=*, itemsep=1.0em, topsep=0.8em]
  \item A movie theater sold 120 tickets. Adult tickets cost \$12 and student tickets cost \$8. The total revenue was \$1{,}240. How many of each ticket were sold?
  \item Two numbers have sum 42 and difference 6. Find the numbers.
  \item A mixture is made with \$3 per pound nuts and \$7 per pound nuts. A 20 lb mix costs \$110. How many pounds of each type?
  \item A taxi charges a \$4 start fee plus \$2.50 per mile. Another company charges \$1.50 per mile with no start fee. For what distance do the costs match?
  \item A school bought 15 calculators and 12 rulers for \$486. Calculators cost \$30 each and rulers cost \$3 each. Verify if the purchase total is possible; if not, find the correct total for those quantities.
  \item A rectangle has perimeter 54 cm. Its length is 3 cm more than twice its width. Find its dimensions.
  \item A farmer sold 68 pounds of apples. Some were sold at \$2 per pound and the rest at \$3 per pound. The total revenue was \$176. How many pounds were sold at each price?
  \item A cell plan costs \$25 per month plus \$0.10 per text. Another plan costs \$35 per month plus \$0.05 per text. For how many texts do the plans cost the same?

  \item A function is given by $f(x)=3x+2$. A plant is 8 cm tall at day 2. Interpret the slope and find the day when the plant is 26 cm tall.
  \item The table shows a function $g$:
  \[
  \begin{array}{c|ccccc}
  x & -2 & -1 & 0 & 1 & 3\\ \hline
  g(x) & 5 & 3 & 1 & 3 & 9
  \end{array}
  \]
  State the domain and range.
  \item A car rental costs \$45 per day plus \$0.20 per mile. Write a function for total cost and find the cost for 3 days and 120 miles.
  \item A function is defined by $h(x)=\dfrac{2x-5}{x+1}$. State the domain in set notation.
  \item A subscription cost is modeled by $C(t)=120-4t$ for $0\le t\le 20$. State the range of $C$.
  \item A function is given by $p(x)=x^2-6x+5$. Find the minimum value and the $x$-value where it occurs.
  \item A function is given by a rule: for each $x$, the output is three less than twice the input. Write the function and evaluate it at $x=-4$.
  \item The table shows a function $m$:
  \[
  \begin{array}{c|cccc}
  x & 0 & 2 & 4 & 6\\ \hline
  m(x) & 7 & 3 & -1 & -5
  \end{array}
  \]
  Determine the average rate of change from $x=0$ to $x=6$, and state the domain.
\end{enumerate}

\end{document}
