\documentclass[12pt]{article}
\usepackage{amsmath, amssymb}
\usepackage{geometry}
\usepackage{enumitem}
\geometry{margin=1in}

\title{Algebra 1 Practice: Proportions and Quadratic Equations}
\author{}
\date{}

\begin{document}
\maketitle

\section*{Instructions}
Our next unit will be Proportional Relationships. This unit is a combination of work from Singapore Math (Chapter 5) and Open Up Resources (Units 1-3). The standards-based score for both units will be assessed by a variety of key assignments, Exit Tickets, assessments, and possible performance tasks.

Complete in 30 minutes. Give exact answers (fractions, radicals) unless a decimal is requested.

\section*{Formulas}
\begin{itemize}[leftmargin=1.5em]
  \item Quadratic formula: for $ax^2+bx+c=0$, $x=\dfrac{-b\pm\sqrt{b^2-4ac}}{2a}$.
  \item Proportion: two ratios are equal, $\dfrac{a}{b}=\dfrac{c}{d}$ with $b\ne0$, $d\ne0$.
  \item Cross-products property: if $\dfrac{a}{b}=\dfrac{c}{d}$, then $ad=bc$.
\end{itemize}

\section*{Problems}
\begin{enumerate}[leftmargin=*, itemsep=1.0em, topsep=0.8em]
  \item Solve: $x^2 - 9x + 18 = 0$.
  \item Solve: $3x^2 + 5x - 2 = 0$.
  \item Solve: $x^2 - 11x + 24 = 0$.
  \item Solve: $2x^2 - 7x + 3 = 0$.
  \item Solve: $x + \dfrac{1}{x} = 2$.
  \item Solve: $x + \dfrac{1}{x} = -3$.
  \item Solve: $x^2 + 6x + 1 = 0$.
  \item Solve: $5x^2 - 20 = 0$.

  \item A recipe uses 3 cups of flour for 8 servings. How many cups of flour are needed for 20 servings?
  \item A map scale is 1 inch : 12 miles. Two towns are 7.5 inches apart on the map. What is the actual distance?
  \item A store sells 6 notebooks for \$7.80. Find the unit price per notebook.
  \item A 2.5 lb bag of rice costs \$4.25. Find the unit price per pound.
  \item A car travels 180 miles in 3 hours at constant speed. How far will it travel in 5 hours?
  \item A mix uses a ratio of 5 parts blue to 3 parts yellow. If there are 24 parts total, how many parts are blue?
  \item A unit price problem: A 12 oz bottle costs \$3.75. A 20 oz bottle costs \$5.60. Which has the lower unit price, and what is that unit price?
  \item A proportional relationship passes through $(4,10)$. Find the constant of proportionality and the equation.
\end{enumerate}

\end{document}
