\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{geometry}
\geometry{margin=1in}

\title{Algebra Assessment: Equations and Proportional Relationships}
\author{}
\date{}

\begin{document}
\maketitle

\section*{Instructions}
Complete all problems. Show clear work. Aim to finish in 30 minutes. Use exact values when radicals appear.

\section*{Context}
Quadratic formula: For $ax^2 + bx + c = 0$ with $a \neq 0$, the solutions are
\[
x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}.
\]
Proportional relationships: Two quantities $x$ and $y$ are proportional if $\dfrac{y}{x} = k$ (a constant), so $y = kx$. Example: If 3 books cost \$12, then $k = \dfrac{12}{3} = 4$ dollars per book, so 7 books cost $y = 4 \times 7 = \$28$.

\section*{Problems}
\begin{enumerate}
  \item Solve for $x$: $7x - 5 = 4x + 22$.
  \item Solve for $x$: $3(2x - 1) = 5 - (x + 4)$.
  \item Solve $x^2 - 9x + 18 = 0$.
  \item Solve $4x^2 - 49 = 0$.
  \item Solve $5x^2 + 30 = 0$.
  \item Solve $2x^2 - 3x - 8 = 0$ using the quadratic formula.
  \item A recipe uses 12 cups of water for 8 servings. How many cups of water are needed for 14 servings?
  \item Two quantities are proportional. When $x = 18$, $y = 27$. Find $y$ when $x = 30$.
  \item A graph passes through $(2, 9)$ and represents a proportional relationship. Give the constant of proportionality and the equation relating $y$ and $x$.
  \item A store sells 5 notebooks for \$8.75. At the same rate, what is the price for 18 notebooks?
  \item In a science lab, 45 grams of a substance produce 60 mL of solution. If the relationship is proportional, how many grams are needed for 160 mL?
  \item A class plans a field trip. The cost is directly proportional to the number of students. If 24 students pay \$180 in total, what is the total cost for 31 students?
\end{enumerate}

\end{document}
