\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{enumitem}
\geometry{margin=1in}

\title{Algebra 1 Practice: Statistics, Probability, and Review}
\author{}
\date{}

\begin{document}
\maketitle

\section*{Instructions}
Complete in 30 minutes. Show clear work. Simplify answers when possible. Round probabilities or decimal answers only if a problem asks for it.

\section*{Reference Facts}
\begin{itemize}[leftmargin=1.5em]
  \item Mean $=$ sum of the data values divided by the number of data values.
  \item Median $=$ middle value of an ordered data set.
  \item Range $=$ greatest value $-$ least value.
  \item Interquartile range: $\mathrm{IQR}=Q_3-Q_1$.
  \item Probability of an event:
  \[
  P(\text{event})=\frac{\text{number of favorable outcomes}}{\text{number of possible outcomes}}.
  \]
\end{itemize}

\section*{Problems}
\begin{enumerate}[leftmargin=*, itemsep=1em, topsep=0.8em]
  \item The data set is
  \[
  6,\ 11,\ 9,\ 14,\ 11,\ 7,\ 5,\ 12,\ 9.
  \]
  Find the mean, median, mode, and range.

  \item The data set is
  \[
  3,\ 8,\ 8,\ 9,\ 10,\ 12,\ 15,\ 18,\ 21,\ 24,\ 30.
  \]
  Find $Q_1$, $Q_3$, and the interquartile range.

  \item A data set has mean 18 for 7 values. Six of the values are
  \[
  9,\ 14,\ 16,\ 18,\ 20,\ 25.
  \]
  Find the seventh value.

  \item The five-number summary of a data set is
  \[
  \min=4,\quad Q_1=9,\quad \text{median}=13,\quad Q_3=18,\quad \max=27.
  \]
  Draw a box-and-whisker plot and state the range and IQR.

  \item The ordered data set is
  \[
  2,\ 5,\ 6,\ 6,\ 8,\ 10,\ 11,\ 13,\ 15,\ 18,\ 21,\ 23.
  \]
  If 30 is added to the data set, which measures change: mean, median, range, IQR? Find the new mean and new range.

  \item A spinner has 8 equal sections numbered 1 through 8. What is the probability of spinning
  \[
  \text{an even number,}\qquad
  \text{a number greater than 5,}\qquad
  \text{an odd number less than 6}?
  \]

  \item A bag contains 5 red marbles, 4 blue marbles, and 3 green marbles. One marble is chosen at random. Find the probability that the marble is
  \[
  \text{blue,}\qquad
  \text{not green,}\qquad
  \text{red or green}.
  \]

  \item You flip a coin and roll a standard six-sided die. How many possible outcomes are there? What is the probability of getting heads and an even number?

  \item How many different two-letter arrangements can be made using the letters A, B, C, and D if no letter may be repeated?

  \item A cafeteria offers 3 sandwich choices, 4 drink choices, and 2 side choices. How many different lunch combinations are possible if one of each is chosen?

  \item Solve:
  \[
  4(2x-3)-5(x+1)=3x-19.
  \]

  \item Solve:
  \[
  x^2-7x+10=0.
  \]

  \item Solve:
  \[
  x+\frac{1}{x}=5.
  \]

  \item The length of a rectangle is 5 more than twice its width, and the area is 48 square units. Find the dimensions of the rectangle.
\end{enumerate}

\end{document}
